---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pteridocat

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/474876749.svg)](https://zenodo.org/badge/latestdoi/474876749)
<!-- badges: end -->

The goal of pteridocat is to provide a taxonomic database of pteridophytes that 
adheres to [Darwin Core standards](https://dwc.tdwg.org/).

## Installation

You can install pteridocat from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("fernphy/pteridocat")
```

## Usage

This package consists of a single data object, a taxonomic database of 
pteridophytes called `pteridocat`.

The `tibble` package is recommended for pretty printing.

```{r example, eval = TRUE}
library(pteridocat)
library(tibble)

pteridocat
```

Run `help(pteridocat)` to see more details about the data.

## Where do these data come from?

The data were downloaded from the 
[Catalog of Life](https://www.catalogueoflife.org/) and modified under the 
[Creative Commons Attribution (CC BY) 4.0](https://creativecommons.org/licenses/by/4.0/) 
license. They were originally compiled by Michael Hassler, who maintains the 
[World Ferns database](https://www.worldplants.de/world-ferns/ferns-and-lycophytes-list),
and generously contributed them to 
[Catalog of Life](https://www.catalogueoflife.org/).

## Citing the data

If you use this package, please cite it! Here is an example:

    FTOL working group. (2022). pteridocat: A taxonomic database of pteridophytes. https://doi.org/10.5281/zenodo.6388786

The example DOI above is for the overall package.

Here is the latest DOI, which you should use if you are using the latest
version of the package:

[![DOI](https://zenodo.org/badge/474876749.svg)](https://zenodo.org/badge/latestdoi/474876749)

You can find DOIs for older versions by viewing the "Releases" menu on
the right.

You should also cite the [World Ferns database](https://www.worldplants.de/world-ferns/ferns-and-lycophytes-list) (contained in [Catalog of Life](https://www.catalogueoflife.org/)), which forms the basis for `pteridocat`:

    Hassler, M. (2021). Checklist of Ferns and Lycophytes of the World. In O. Bánki, Y. Roskov, M. Döring, G. Ower, L. Vandepitte, D. Hobern, D. Remsen, P. Schalk, R. E. DeWalt, M. Keping, J. Miller, T. Orrell, R. Aalbu, R. Adlard, E. Adriaenssens, C. Aedo, E. Aescht, N. Akkari, M. A. Alonso-Zarazaga, et al., Catalogue of Life Checklist (12.8, Dec 2021). https://doi.org/10.48580/d4tm-3dc

## License

- [GPL v3.0](LICENSE.md)

[CC BY-SA 4.0 is one-way compatible with GPL v3.0](https://creativecommons.org/share-your-work/licensing-considerations/compatible-licenses/).
