---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pteridocat

<!-- badges: start -->
<!-- badges: end -->

The goal of pteridocat is to provide a taxonomic database of pteridophytes that adheres to [Darwin Core standards](https://dwc.tdwg.org/).

## Installation

You can install pteridocat from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("joelnitta/pteridocat")
```

## Usage

The taxonomic database is provided as a tibble:

```{r example, eval = TRUE}
library(pteridocat)
library(tibble)

pteridocat
```

Run `help(pteridocat)` to see more details about the data.

## Where do these data come from?

The data were downloaded from the [Catalog of Life](https://www.catalogueoflife.org/) and
modified according to code in (data-raw/pteridocat.R)[data-raw/pteridocat.R] under the 
[Creative Commons Attribution (CC BY) 4.0](https://creativecommons.org/licenses/by/4.0/) license.
They were originally compiled by Michael Hassler, who maintains the [World Ferns
database](https://www.worldplants.de/world-ferns/ferns-and-lycophytes-list), and
generously contributed them to Catalog of Life.

## Licenses

- Code: [MIT](LICENSE.md)
- `pteridocat` dataset: [Creative Commons Attribution (CC BY) 4.0](https://creativecommons.org/licenses/by/4.0/)
