---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pteridocat

<!-- badges: start -->
<!-- badges: end -->

The goal of pteridocat is to provide a taxonomic database of pteridophytes that 
adheres to [Darwin Core standards](https://dwc.tdwg.org/).

## Installation

You can install pteridocat from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("joelnitta/pteridocat")
```

## Usage

This package consists of a single data object, a taxonomic database of 
pteridophytes called `pteridocat`.

The `tibble` package is recommended for pretty printing.

```{r example, eval = TRUE}
library(pteridocat)
library(tibble)

pteridocat
```

Run `help(pteridocat)` to see more details about the data.

## Where do these data come from?

The data were downloaded from the 
[Catalog of Life](https://www.catalogueoflife.org/) and modified under the 
[Creative Commons Attribution (CC BY) 4.0](https://creativecommons.org/licenses/by/4.0/) 
license. They were originally compiled by Michael Hassler, who maintains the 
[World Ferns database](https://www.worldplants.de/world-ferns/ferns-and-lycophytes-list),
and generously contributed them to 
[Catalog of Life](https://www.catalogueoflife.org/).

## License

[GPL v3.0](LICENSE.md)

[CC BY-SA 4.0 is one-way compatible with GPL v3.0](https://www.gnu.org/licenses/license-list.en.html).
